\section{Contributions}

Many people were involved in the making of this research. Additionally, much of 
this research has been published or submitted for consideration at a publisher.  
This thesis will therefore include components which have been published or were 
done by other researchers. This section will outline the contributions of 
everyone and any relevant publications (pending or otherwise), so no work is 
misrepresented.

Chad C. Williams, Dr. Olav E. Krigolson, and others from the Neuroeconomics Lab 
at the University of Victoria collected the data for this thesis and performed 
the EEG preprocessing in coordination with us. Chad performed the reward 
positivity analysis on the data as well. Their EEG expertise was invaluable 
through many components of the project. The word vectors for this thesis were 
trained and provided by wordvectors.org. The work in Appendix A was done in 
equal collaboration with Dhanush Dharmaretnam, Haoyan Xu, and with mentorship 
from Dr. George Tzanetakis.  The work in Appendix B was largely completed by 
Dhanush Dharmaretnam, while our contribution was the adversarial component of 
the research. Throughout the entirety of the novel research described in this 
document Dr. Alona Fyshe provided continueing mentorship, guidance, feedback, 
and ideas.

An early version of the work in this thesis was published at the Inaugural 
Conference on Cognitive Computational Neuroscience. A complete version of the 
work in this thesis has been submitted for consideration at the journal 
NeuroImage. Appendix A is pending publication at the IEEE 20th International 
Workshop on Multimedia Signal Processing. Appendix B has been submitted for 
consideration at the Thirty-second Annual Conference on Neural Information 
Processing Systems.
