\section{Time Windowing Analysis}
The Time Windowing Experiment separated the averaged trial data into 50ms 
windows and evaluated the model pipeline on each window. We had hypothesized 
that our time analysis would see a delayed peak response compared to prior 
work~\cite{Sudre2012} due to the additional processing time required to map 
from the symbol language to the English word. We found a peak accuracy in the 
600-650ms window with a 2 vs 2 accuracy of 74.57\%. Previously, a similar 
experiment using MEG data that did not utilize a symbol mapping component found 
a peak accuracy of 350ms-400ms~\cite{Sudre2012}. This delay appears to be 
present in our results, and slows the emergence of semantic representations by 
about 250ms. This provides evidence that the newly formed mapping delays 
retrieval by about a quarter of a second.

Interestingly, very little \tvt accuracy is lost when we evaluated our model 
using only a small window (50ms) compared to our initial experiment (Section 
~\ref{sec:discussion:semanticrepresentation}) which used a much longer window 
(700ms). By windowing the exposure we remove the majority of data provided to 
the regression models, but see only a minimal reduction in accuracy (5\%). This 
is notable since a model with significantly fewer parameters is much faster to 
train and evaluate.

We also see a large, statistically significant spike in \tvt accuracy early in 
time, around 125ms-200ms. Sudre et al. had also found statistically significant 
accuracy early in the processing pipeline, but had determined this to be 
heavily correlated to the visual features of the words they presented rather 
than the semantics of the words~\cite{Sudre2012}. Our experiment, however, 
should not experience the same correlation with visual features such as 
\emph{Word Length} or \emph{Image Diagonalness} as we use an arbitrary mapping 
of words to symbols (discussed in 
Section~\ref{sec:discussion:semanticrepresentation}). It is notable that 
studies have shown evidence of semantics much earlier in time, such as Moseley 
et al. who were able to differentiate between semantic categories as early as 
150ms into the exposure~\cite{moseley2013sensorimotor}. There are several key 
difference between this experiment and Sudre et al..  First, our experiment 
uses Skipgram instead of vectors based on behavioral responses to semantic 
questions. The Skipgram method, based on word co-location, encodes semantics 
differently than the behavioral response vectors, and may model some component 
of semantic representations that is available earlier in time.  Second, our 
experiment uses multiple parts of speech, whereas the original Sudre et al. 
used only concrete nouns.  Perhaps part of speech identity is differentiable 
early in time, which would not have been detectable in an experiment using only 
nouns.  Third, the task performed by our participants is much more interactive 
and requires engagement learning.  The Sudre et al. task was a simple semantic 
question answering task. Perhaps a more engaging task evokes a faster or more 
consistent neural response.  Each of these differences may be the reason we see 
such early semantic activation.  We will need further experiments to determine 
if this early semantic signal is replicable, and if it is truly correlated to 
very early semantic recall.

The display of the four word options at 500ms is likely to have an effect on 
the timeline of these results as well. At the initial display, participants 
attempted to translate the symbol to an unknown word. With the addition of the 
four options at 500ms, participants had a narrowed down option set of only four 
words to map to. This may lead to the appearance of two accuracy spikes: one of 
early semantics shortly after the initial stimuli and one of confirmation after 
the four word appearance at 500ms. We can still confirm that the mapping is 
being measured in both cases, rather than the word, due to the differences in 
\tvt accuracy between earlier and later exposures of the same word as seen in 
the Participant Learning experiment discussed in 
Section~\ref{sec:results:participantlearning}.
