\section{Measurement of Participant Learning}
One of the exciting and unique attributes of this experiment paradigm compared 
to other experiments in semantic reepresenation research was the introduction 
of an artificial language through a learning task. This allows us to research 
and understand how the semantic representation develops in the brain during 
participants' learning. We therefore hypothesized that the \tvt accuracy would 
increase in later exposures for a given word as participants learn.

Our Participant Learning Experiment measured the strength of semantic 
representation at different exposure counts for individual words, and found 
that semantic representation of a symbol emerges after or near the 4th trial.  
The average of trials (4, 5, 6) produced 2 vs 2 accuracy of 72.35\%, which is 
significantly above chance with $p < 0.001$ (FDR corrected). This is evidence 
that the symbol mapping is learned very quickly, within only a few exposures.  
We see this effect in both the 0 - 700 ms time period and 0 - 500 ms time 
period.

Previous work has detected participant learning by grouping trials together and 
measuring the reward positivity~\cite{krigolson2014we}. However, reward 
positivity does not always coincide with learning-related behavioral changes 
(i.e. task accuracy), making it potentially unclear if reward positivity is 
related to a direct brain function for learning or if reward positivity is an 
indirect effect from a brain function related to 
feedback~\cite{walsh2012learning}. Recent work has made new arguments 
supporting the view that reward positivity is a direct index of neural 
learning~\cite{williams2017application}. 

Our work provides another angle for comparison, as we measured learning by 
detecting the actual \emph{concept} to be learned (i.e. the word vector) rather 
than using an indirect measurement via an ERP. This supports the claim that 
reward positivity is directly related to a brain function for learning, or at 
least indicates evidence for a negative correlation with \tvt accuracy. That 
is: the reward positivity response decreases in amplitude as the representation 
for the concepts being learned increases in \tvt accuracy.

In addition to providing support for the reward positivity, our model has 
benefits over the traditional analysis method in many paradigms. Since our 
model detects the semantic representation, it can be used to model both the 
process of learning and the later retention of learning.  Reward positivity can 
show when learning has occurred, but the absence of reward positivity does not 
indicate the knowledge of the topic.  Thus, our approach could offer benefits 
in experiments where it is important to measure \emph{retention} of the 
mapping.

A further benefit of our approach is assessment of the speed of learning, in 
addition to detecting learning processes. Previous literature in learning 
detected only the presence of learning, but did not aim to quantify the speed 
at which learning occurs~\cite{krigolson2014we}. Our work shows learning as it 
occurs over the averaged trials, even in a fairly complicated experimental 
paradigm. This can additionally be more useful than using task accuracy alone 
to measure learning, as task accuracy cannot detect guessing. Future 
experiments may find new insight when researching learning by leveraging the 
more complete picture provided by considering \tvt accuracy.
