\section{Semantic Representation Experiment}
\label{sec:experiments:semanticrepresentation}

When the participants initially viewed the symbols, they did not know the 
English equivalent. But, as they learned the symbol mapping through trial and 
error, semantic understanding developed. Our methodology allows us to test if 
word semantics are correlated to EEG activity while viewing the corresponding 
symbol, and this first experiment is the simplest test of the methodology. We 
hypothesized that we would see statistically significant accuracy when training 
on trials after learning is assumed to have occurred.

For each participant, we removed symbols that were presented less than six 
times to that participant, and removed the first two exposures of each symbol 
for each participant (as we can assume the symbols were not associated with a 
semantic meaning in the first two trials). The parameters for trial selection 
(two and six) provide a balance between allowing the participant time to learn 
the word, while also retaining enough data to train our model. We expected 
longer trial lengths to have higher accuracy, as it includes more time for the 
participants to think about the translation, but we also do not want to include 
muscle artifacts. Therefore, we cut trials to 700 ms in length to avoid 
including muscle signals in the exposure after the appearance of word choices 
at 500 ms (as the shortest response time was 248 ms).  We also test with trials 
cut to 500 ms to compare the \tvt accuracy when the appearance of word choices 
is excluded from the exposure, to verify that we are not inadvertently 
identifying the semantics of the displayed words.  We then averaged the 
remaining exposures over all participants for each word, which gave us a single 
noise-reduced exposure per word. This data was used to train regression models 
and perform the \tvt test. 

This experiment is the closest to previous work in other modalities, and 
functions as our baseline validation of the experiment methodologies discussed 
in the previous chapter. The data extracted is intended to be representative of 
words the participants have learned the mapping for, although it will not be 
identical to the task of reading English words as the participants must still 
perform the cognitive task of correctly identifying the mapping for the symbol.  
A statistically significant \tvt accuracy in this experiment indicates that we 
can correctly identify the semantic representations of the mapped English words 
in EEG.
